\documentclass[addpoints]{exam}

\usepackage{amsmath,amssymb, amsthm}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\usepackage{forest}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{wasysym}
\usepackage{mdframed}
\usepackage{arabtex}
\usepackage{utf8}
\setcode{utf8}


% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS 212, Fall 2024}{HW 3: Turing Machine, $\ldots$, Recognizability}{Fall 2024}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

\newcommand{\blank}{\textvisiblespace}

\boxedpoints
% \printanswers %uncomment this

\title{Turing Machine, Variants, Decidability, and Recognizability\\ \vspace{0.5cm} \Large CS 212 Nature of Computation\\Habib University}
\author{Blingblong} %Enter your team name here
\date{Fall 2024}

\begin{document}
\maketitle

\begin{questions}

    \question[10] Let $\Gamma = \{0, 1, \blank\}$ be the tape alphabet for all Turing Machines in this problem. 
    
    After failing to show off your intellect to your peers you have reached a preschool, where you have decided to participate in the ongoing playground competition of saying the largest number you know. After going back and forth with some second graders, to show off your superior mathematical intellect, you say \href{https://en.wikipedia.org/wiki/Googolplex}{Googolplex}, to this an overly smart kid says the \href{https://en.wikipedia.org/wiki/Graham%27s_number}{Graham's number}. You being more competitive than any other seven year old there says \textsc{tree}(3). Little known to you a seven grader grown on Numberblock, Baby Shark and Skibidi Toilet defines a very peculiar function, called the Working Bidoof. 
    Working Bidoof $WB : \mathbb{N} \to \mathbb{N}$ is defined as follows. For any $k \in \mathbb{N}$, $WB(k)$ is the maximum of 1s remaining on the Tape among all possible $k$-state Turing machines that Halts when starting with a blank tape. In other words let $WB(k) = \max(\{n \in \mathbb{N}|\;$ a $k$-state turing machine Halts with $n$ 1s on the tape$\})$. 

    Show that function Working Bidoof $WB$ is not computable.
    
    \begin{solution}
        %enter your solution here
    \end{solution}
    
    \question[10] An $\textit{Euclidean-Space}$ Turing machine has the usual finite-state control but a tape that extends in a three-dimensional grid of cells, infinite in all directions. Both the head and the first input symbol are initially placed at a cell designated as the origin. Each consecutive input symbol is in one of the six neighboring cells and does not overwrite a previous symbol. The head can move in one transition to any of the six neighboring cells. All other workings of the Turing machine are as usual.
    
    Provide a formal description of the \textit{Euclidean-Space} Turing Machine and prove that it is equivalent to an ordinary Turing machine. Recall that two models are equivalent if each can simulate the other.
    
    \begin{solution}
        %enter your solution here
    \end{solution}
      
    \question[10] Let \textsc{non-regular} = $\{L \subseteq \Sigma^*|\; L$ is decidable but $L$ is not regular $\}$. 
    Show that every element of \textsc{non-regular} contains an unrecognizable subset.
    \begin{solution}
        %enter your solution here
    \end{solution}
    \end{questions}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
